Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-03 paper/paper.qmd
commit changes to paper.qmd

library(tidyverse)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(usmap)
library(arrow)
library(knitr)
library(Matrix)
library(splines)
library(kableExtra)
library(broom.mixed)
library(brms)

@@

To give an overview of the outcome variable, divided per candidate, we provide summary statistics of this key variable, highlighting the characteristics of the polling support for each candidate across the battleground states. 
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-outcomevar
#| fig-cap: "Summary Statistics for Trump and Harris Polling Data - Presents key summary statistics, including total polls, average support percentages, and the maximum and minimum polling levels for both candidates across the specified battleground states. All values are rounded to three decimal places, providing an overview of the polling landscape as of the selected election date."

@@

# Results {#sec-results}
## State-Level Polling Averages for Trump and Harris
WRITE - explain why we are showing this average table first and what the table reveals
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-stateaverage
#| fig-cap: "Table displaying the percentage of support for Donald Trump and Kamala Harris across key battleground states in the lead-up to the 2024 United States Presidential Election. The table lists states with their respective support percentages, highlighting the competitive landscape as voters prepare to make their decisions on Election Day. Notably, Trump maintains a slight lead in states such as Arizona and Georgia, while Harris shows stronger support in states like Michigan and Nevada. This data provides insight into the current polling dynamics and potential electoral outcomes in these critical states."

@@

## Probability of Winning by State on Election Day 
@tbl-state-probabilities displays the numeric percentage of the probabilities of winning for Trump and Harris. By comparing the predicted probabilities, the predicted winner for each state is assigned accordingly. For instance, the table displays that Trump has a 49.48% predicted probability of winning Arizona compared to 49.24% of Harris’s, making Trump the predicted winner in Arizona. For all six other states, Harris has a higher predicted probability of winning than Trump.
```{r}
#| echo: false
#| eval: true
#| label: tbl-state-probabilities
#| fig-cap: "Probability of Trump Winning by State on Election Day."
#| warning: false

>>>>

# Workplace SetUp
library(tidyverse)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(usmap)
library(arrow)
library(knitr)
library(Matrix)
library(splines)
library(kableExtra)
library(broom.mixed)
library(brms)

@@

To give an overview of the outcome variable, divided per candidate, we provide summary statistics of this key variable, highlighting the characteristics of the polling support for each candidate across the battleground states. 
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-outcomevar
#| tbl-cap: "Summary Statistics for Trump and Harris Polling Data - Presents key summary statistics, including total polls, average support percentages, and the maximum and minimum polling levels for both candidates across the specified battleground states. All values are rounded to three decimal places, providing an overview of the polling landscape as of the selected election date."

@@

# Results {#sec-results}
## State-Level Polling Averages for Trump and Harris
WRITE - explain why we are showing this average table first and what the table reveals
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-stateaverage
#| tbl-cap: "Table displaying the percentage of support for Donald Trump and Kamala Harris across key battleground states in the lead-up to the 2024 United States Presidential Election. The table lists states with their respective support percentages, highlighting the competitive landscape as voters prepare to make their decisions on Election Day. Notably, Trump maintains a slight lead in states such as Arizona and Georgia, while Harris shows stronger support in states like Michigan and Nevada. This data provides insight into the current polling dynamics and potential electoral outcomes in these critical states."

@@

## Probability of Winning by State on Election Day 
@tbl-state-probabilities displays the numeric percentage of the probabilities of winning for Trump and Harris. By comparing the predicted probabilities, the predicted winner for each state is assigned accordingly. For instance, the table displays that Trump has a 49.48% predicted probability of winning Arizona compared to 49.24% of Harris’s, making Trump the predicted winner in Arizona. For all six other states, Harris has a higher predicted probability of winning than Trump.
```{r}
#| echo: false
#| eval: true
#| label: tbl-state-probabilities
#| tbl-cap: "Probability of Trump Winning by State on Election Day."
#| warning: false
